---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Cori Jaskiewicz"
date: "8/26/2019"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

*How many rows and how many columns does the datasaurus_dozen file have?*\
A data frame with 1846 rows and 3 variables. The variables are **dataset**, **x**, and **y**.

### Exercise 2

*Plot* **x** *vs.* **y** *for the  dino dataset. Then, calculate the correlation coefficient between* `x` *and* `y` *for this dataset.*

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
The correlation between `x` and `y` is -0.0645.\

### Exercise 3

*Plot* **x** *vs.* **y** *for the star dataset. Then, calculate the correlation coefficient between* `x` *and* `y` *for this dataset.*

First let's plot the data in the star dataset:


```{r plot-star, fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

The correlation between `x` and `y` is -0.0630. This correlation is closer to zero so it is a slightly worse correlation.\

### Exercise 4

*Plot* **x** *vs.* **y** *for the circle dataset. Then, calculate the correlation coefficient between* `x` *and* `y` *for this dataset.*

First let's plot the data in the circle dataset:


```{r plot-circle, fig.height=3, fig.width=6}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

The correlation between `x` and `y` is -0.0683. This correlation is further from zero / closer to -1 so it is a slightly better correlation.\

### Exercise 5

First let's plot all the data at once:

```{r plot-all, fig.height=9, fig.width=12}
ggplot(data = datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() + facet_wrap(~ dataset, ncol = 3) + theme(legend.position = "none")

datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```